Hypercoercions and a Framework for Equivalence of Cast Calculi

### 2019-10-19 paper.tex
revise text of 4.1

	Reduction \fbox{$ \judgeCreduce{s}{s} $}
	\[
	\begin{array}{rclr}
		\redrule{
		\sOOinspect{\eOOcast{e}{T_1}{l}{T_2}}{\rho}{\kappa}
	}{
		\sOOinspect{e}{\rho}{\langle\cOOcast{T_1}{l}{T_2}\rangle\kappa}
	}{}

	\redrule{
		\sOOinspect{\eOOvar{x}}{\rho}{\kappa}
	}{	
		\sOOreturn{\rho[x]}{\kappa}
	}{}
	\redrule{
		\sOOinspect{\eOOsole}{\rho}{\kappa}
	}{
		\sOOreturn{\vOOtt}{\kappa}
	}{}
	\redrule{
		\sOOinspect{\eOOlam{T_1}{T_2}{x}{e}}{\rho}{\kappa}
	}{
		\sOOreturn{(\vOOfun{\rho}{x}{e})}{\kappa}
	}{}
	\redrule{
		\sOOinspect{(\eOOcons{e_1}{e_2})}{\rho}{\kappa}
	}{
		\sOOinspect{e_1}{E}{}
	}{}
	\redrule{
		\sOOinspect{(\eOOinl{e})}{\rho}{\kappa}
	}{
		\sOOinspect{e}{\rho}{(\kOOinl{\kappa})}
	}{}
	\redrule{
	\sOOinspect{(\eOOinr{e})}{\rho}{\kappa}
	}{
	\sOOinspect{e}{\rho}{(\kOOinr{\kappa})}
	}{}
	\redrule{
		\sOOinspect{(\eOOapp{e_1}{e_2})}{\rho}{\kappa}
	}{
\sOOinspect{e_1}{\rho}{(\kOOappI{E}{e_2}{\kappa})}}{}

@@

After showing their cast representation is a Lazy D Cast, users of our 
frameworks can plug-in this cast representation to our space-efficient abstract 
machine in subsection~\ref{ssec:framework:cek}, and prove that this machine is 
equivalent to \ineffCEKD subsection~\ref{secc:framework:all-correct}, which 
depends on lemmas in subsection~\ref{secc:framework:monoid-correct}.

@@

Let $ v $ range over value. 
In \ineffCEK\, we have one value constructor for all casted value.
In \effCEK{C}, however, we do not have this generic value constructor, 
instead we push those casts into the value constructors most of the time and 
use $ \hcvOOinj{P}{v} $ to construct values casted to $ \TOOdyn $.
Non-casted values in \ineffCEK\ correspond to values in \effCEK{C} where the 
casts are identity (i.e. constructed by $ id(T) $).

@@

Let $ \kappa $ range over continuations and let $ k $ range over 
pre-continuations. 
A continuation is now a pre-continuation prefixed with a cast.
Pre-continuation are like the continuations in \ineffCEK.
In \ineffCEK\, a continuation have zero or more casts at the top.
In \effCEK{C}, however, every continuation has exactly one cast at the top.
Continuations in \ineffCEK\ that have no casts at the top correspond to 
continuations in \effCEK{C}\ whose casts are identity.
And continuations in \ineffCEK\ that have many casts at the top correspond to 
continuations in \effCEK{C}\ where those casts are composed by $ 
seq(c,c) $.

@@

Transitive closure of reduction ($ \judgeSreduceTrans{C}{s}{s} $) and 
evaluation are standard. Value typing ($ \judgeType{v}{T} $) is straightforward.

>>>>

	Reduction \fbox{$ \judgeCreduce{s}{s} $}
	\[
	\begin{array}{rclr}
		\redrule{
		\sOOinspect{\eOOcast{e}{T_1}{l}{T_2}}{\rho}{\kappa}
	}{
		\sOOinspect{e}{\rho}{\langle\cOOcast{T_1}{l}{T_2}\rangle\kappa}
	}{}
	\redrule{
		\sOOinspect{\eOOvar{x}}{\rho}{\kappa}
	}{	
		\sOOreturn{\rho[x]}{\kappa}
	}{}
	\redrule{
		\sOOinspect{\eOOsole}{\rho}{\kappa}
	}{
		\sOOreturn{\vOOtt}{\kappa}
	}{}
	\redrule{
		\sOOinspect{\eOOlam{T_1}{T_2}{x}{e}}{\rho}{\kappa}
	}{
		\sOOreturn{(\vOOfun{\rho}{x}{e})}{\kappa}
	}{}
	\redrule{
		\sOOinspect{(\eOOcons{e_1}{e_2})}{\rho}{\kappa}
	}{
		\sOOinspect{e_1}{E}{}
	}{}
	\redrule{
		\sOOinspect{(\eOOinl{e})}{\rho}{\kappa}
	}{
		\sOOinspect{e}{\rho}{(\kOOinl{\kappa})}
	}{}
	\redrule{
	\sOOinspect{(\eOOinr{e})}{\rho}{\kappa}
	}{
	\sOOinspect{e}{\rho}{(\kOOinr{\kappa})}
	}{}
	\redrule{
		\sOOinspect{(\eOOapp{e_1}{e_2})}{\rho}{\kappa}
	}{
\sOOinspect{e_1}{\rho}{(\kOOappI{E}{e_2}{\kappa})}}{}

@@

After showing their cast representation is a Lazy D Cast, users of our 
frameworks can plug-in this cast representation to our space-efficient abstract 
machine in subsection~\ref{ssec:framework:cek}, and prove that this machine is 
equivalent to \ineffCEKD\ (subsection~\ref{secc:framework:all-correct}), which 
depends on lemmas in subsection~\ref{secc:framework:monoid-correct}.

@@

Let $ v $ range over value. 
In \ineffCEK\, we have one value constructor for all casted value.
In \effCEK{C}, however, we do not have this generic value constructor, 
instead we push those casts into the ordinary values. For instance, $ 
(\vOOcons{v_1}{v_2}) $ corresponds to $ 
(\hcvOOcons{v_1'}{id(T_1)}{v_2'}{id(T_2)}) $. To construct values of the 
dynamic type, we use $ (\hcvOOinj{P}{v}) $.

@@

Let $ \kappa $ range over continuations and let $ k $ range over 
pre-continuations. 
A continuation is now a pre-continuation prefixed with a cast.
Pre-continuation are like the continuations in \ineffCEK, but there is no 
constructor for casts.
Continuations in \ineffCEKD\ have zero or more casts at the top.
In \effCEK{C}, however, every continuation has exactly one cast at the top.
Continuations in \ineffCEK\ that have no casts at the top correspond to 
continuations in \effCEK{C}\ whose casts are identity.
And continuations in \ineffCEK\ that have many casts at the top correspond to 
continuations in \effCEK{C}\ where those casts are composed by $ 
seq(c,c) $.

@@

Transitive closure of reduction ($ \judgeSreduceTrans{C}{s}{s} $) and 
evaluation ($ \judgeSeval{C}{e}{o} $) are standard. Value typing ($ 
\judgeType{v}{T} $) is straightforward.
